Fuzzy joins through deep learning

### 2018-07-28 paper2018/siamese_networks.tex
work on figures

\subsection{Loss functions}
\label{loss_functions}
Let $\mathbf{x}$ represent an embedding for an entity name, and $\bf{x_{a}}$, $\bf{x_{p}}$, $\bf{x_{n}}$ reflect the vector embeddings of the \textit{anchor}, \textit{positive} and \textit{negative}, respectively.  We investigated four different loss functions to explore their effectiveness for the entity metric learning problem.
\subsubsection{Triplet loss}

\begin{figure}
\includegraphics[width=0.5\linewidth]{schroff_triplet}
\caption{Triplet loss}
\label{schroff_loss}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.5\linewidth]{modified_loss}
\caption{Modified loss}
\label{modified_loss}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{angular_loss}
\caption{Angular loss}
\label{angular_loss}
\end{figure}

@@

>>>>

\subsection{Loss functions}
\label{loss_functions}

Let $\mathbf{x}$ represent an embedding for an entity name, and $\bf{x_{a}}$, $\bf{x_{p}}$, $\bf{x_{n}}$ reflect the vector embeddings of the \textit{anchor}, \textit{positive} and \textit{negative}, respectively.  We investigated four different loss functions to explore their effectiveness for the entity metric learning problem.

\begin{figure*}[htb]
    \centering
    \begin{subfigure}[t]{0.23\textwidth}
        \centering
        \includegraphics[width=.9\linewidth]{schroff_triplet}
        \caption{Triplet loss}
        \label{schroff_loss}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.23\textwidth}
        \centering 
        \includegraphics[width=.9\linewidth]{modified_loss}
        \caption{Modified loss}
        \label{modified_loss}
    \end{subfigure}
    ~ 
    \begin{subfigure}[t]{0.23\textwidth}
        \centering 
        \includegraphics[width=.9\linewidth]{angular_loss}
        \caption{Angular loss}
        \label{angular_loss}
    \end{subfigure}
    ~ 
    \begin{subfigure}[t]{0.23\textwidth}
        \centering 
        \includegraphics[width=.9\linewidth]{tanh_triplet}
        \caption{$Tanh$ loss}
        \label{tanh_loss}
    \end{subfigure}
    \caption{Loss functions}
\end{figure*}

\subsubsection{Triplet loss}

@@

@@

@@

\subsubsection{Hyperbolic Tangent Loss}
